Parallel Hierarchical Clustering using \\ Rank-Two Nonnegative Matrix Factorization \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-07-01 latex/paper.tex
reformulated hiernmf2 code to use split function (more accurate to actual implementation)

\usepackage{cite,doi}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm,algpseudocode}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{cleveref}
\usepackage{ourmacros}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

test reference: \cite{GKP15}

@@

@@

@@

>>>>

\usepackage{cite,doi}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm,algpseudocode}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{cleveref}
\usepackage{tikz}
\usepackage{ourmacros}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

@@

\begin{itemize}
	\item NMF, BCD, rank-2 NMF
\end{itemize}

@@

\begin{algorithm}
\caption{Hierarchical Clustering \cite{KP13}}
\label{alg:hiernmf2}
\begin{algorithmic}[1]
	\Require{$\M{A}$ is $m\times n$, $k$ is target number of leaves}
	\Function{${\cal T} =$ Hier-R2-NMF}{$\M{A}$}
		\State ${\cal R} = \text{node}(\M{A})$ \hfill \Comment{create root node}
		\State \textsc{Split}$({\cal R})$
		\State inject$({\cal Q},{\cal R}.\text{left})$ \hfill \Comment{create priority queue}
		\State inject$({\cal Q},{\cal R}.\text{right})$ \hfill \Comment{of frontier nodes}
		\While{size$({\cal Q}) < k$}
			\State ${\cal N} = \text{eject}({\cal Q})$ \hfill \Comment{get leaf with max score}
			\State \textsc{Split}$({\cal R}.\text{left})$ \hfill \Comment{split left child}
			\State inject$({\cal Q},{\cal R}.\text{left})$ \hfill \Comment{and add to $\cal Q$}
			\State \textsc{Split}$({\cal R}.\text{right})$ \hfill \Comment{split right child}
			\State inject$({\cal Q},{\cal R}.\text{right})$ \hfill \Comment{and add to $\cal Q$}
		\EndWhile
	\EndFunction
	\Ensure{$\cal{T}$ is binary tree rooted at $\cal R$ with $k$ frontier nodes, each node has subset of cols of $\M{A}$ and feature vector $\V{w}$}
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Node Splitting via Rank-Two NMF}
\label{alg:split}
\begin{algorithmic}[1]
	\Require{$\cal N$ has a subset of columns given by field $\M{A}$}
	\Function{Split}{$\cal N$}
		\State $[\M{W},\M{H}] = \textsc{Rank2-NMF}({\cal N}.\M{A})$ \hfill \Comment{split $\cal N$}
		\State partition ${\cal N}.\M{A}$ into $\M{A}_1$ and $\M{A}_2$ using $\M{H}$
		\State ${\cal N}.\text{left} = \text{node}(\M{A}_1,\V{W}_1)$ \hfill \Comment{create left child}
		\State ${\cal N}.\text{right} = \text{node}(\M{A}_2,\V{W}_2)$ \hfill \Comment{create right child}
		\State ${\cal N}.\text{score} = \sigma_1(\M{A}_1) + \sigma_1(\M{A}_2) - \sigma_1({\cal N}.\M{A})$
	\EndFunction
	\Ensure{$\cal{N}$ has two children and a score}
\end{algorithmic}
\end{algorithm}

@@

\begin{figure}
\input{fig/split}
\caption{Parallel splitting using Rank-2 NMF}
\label{fig:split}
\end{figure}
